Measuring Perceptions and Preferences for Meritocracy

### 2021-01-11 docs/paper.Rmd
corregir mathjax

Table \@ref(tab:invargroup) shows the results of the measurement invariance tests. When attending to the traditional invariance test of $\\Delta \\chi^2 (\\Delta \\text{df})$, the results  support the invariance at the strong level meaning that the fit of the factor model of the PPM-S scale is equivalent across samples when constraining factor loadings and intercepts to being equal. Such results is considered in general as evidence of invariance [citar paper Fischer en SJR], as strict forms of measurement invariance rarely hold [citar van der Schoot et al]. Still, the comparability of latents means requires strict invariance which in this case does not hold using $\\Delta \\chi^2 (\\Delta \\text{df})$. Nevertheless the criteria of $\\Delta \\text{CFI}$ used for comparing models is close to the rejection criteria of >.01, whereas the $\\Delta \\text{RMSEA}$ is below the cut-off criteria suggested by this criteria [citar  @chen 2007 ]. Therefore, the evidence for strict invariance is still not concluding.

>>>>

Table \@ref(tab:invargroup) shows the results of the measurement invariance tests. When attending to the traditional invariance test of $\Delta \chi^2 (\Delta \text{df})$, the results  support the invariance at the strong level meaning that the fit of the factor model of the PPM-S scale is equivalent across samples when constraining factor loadings and intercepts to being equal. Such results is considered in general as evidence of invariance [citar paper Fischer en SJR], as strict forms of measurement invariance rarely hold [citar van der Schoot et al]. Still, the comparability of latents means requires strict invariance which in this case does not hold using $\Delta \chi^2 (\Delta \text{df})$. Nevertheless the criteria of $\Delta \text{CFI}$ used for comparing models is close to the rejection criteria of >.01, whereas the $\Delta \text{RMSEA}$ is below the cut-off criteria suggested by this criteria [citar  @chen 2007 ]. Therefore, the evidence for strict invariance is still not concluding.
